Supplementary Material for 'New insights into the Weddell Sea ecosystem applying

### 2023-10-13 Manuscript/SupMaterial.Rmd
Update Sup Mat with description of alfa estimation

$$
\begin{aligned}
IS = \alpha X_R \frac{m_R}{m_C}\\
\end{aligned}
$$
where $\alpha$ is the search rate, $X_R$ is the resource density, and $m_R$ and $m_C$ are the body mass for the resource and the consumer, respectively [@Pawar2012].

>>>>

$$
\begin{aligned}
IS = \alpha X_R \frac{m_R}{m_C}\\
\end{aligned}
$$
where $\alpha$ is the search rate, $X_R$ is the resource density, and $m_R$ and $m_C$ are the body mass for the resource and the consumer, respectively [@Pawar2012]. We assume the case were resources are scarce because this resembles field conditions, figure 3 e & f and equation 3 from Pawar's paper.
Then the search rate for 2D interactions (see main text) is calculated as

$$\alpha = \alpha_{2D} m_C^{0.68}$$
For 3D interactions is calculated as:

$$\alpha = \alpha_{3D} m_C^{1.05}$$
where $\alpha_{2D}$ and $\alpha_{3D}$ are the intercepts for each interaction dimensionality.

As the resource density $X_R$ is not known we estimated it according to the equation S18 and supplementary figures 2i & j (individuals/m2 - m3)

$$X_R = X_0 m_R^{-p_x}$$

were $p_x$ is -0.79 for 2D and -0.86 for 3D.
